Wall-to-wall mapping of peat depth from Lidar terrain and airborne radiometrics in Norwegian landscapes

### 2024-11-21 ms/ms.Rmd
ms: results - minor edit extrapolation RMSE

When we tested how well models extrapolated from within to outside of mapped peatland, we found that the models produced marginally better RMSE than just assuming a constant \unit{30\,cm} depth (Fig. \@ref(fig:modelMetricsExtrapolation)).
Compared to our error estimates with the full dataset, RMSE at Skrimfjella was nearly unchanged, while at Ørskogfjellet it was lower outside of mapped peatland.
With the independent occurrence data at Skrimfjella, we found that neither the *terrain-only* nor *terrain and radiometric* configurations were able to discriminate between peat presence and absence (area under the curve of the receiver operating characteristic 0.44 and 0.52 respectively, where 0.5 indicates random guessing).

>>>>

When we tested how well models extrapolated from within to outside of mapped peatland, we found that the models produced marginally better RMSE than just assuming a constant \unit{30\,cm} depth (Fig. \@ref(fig:modelMetricsExtrapolation)).
At Skrimfjella RMSE in the extrapolation was nearly the same as RMSE across all land cover types.
At Ørskogfjellet RMSE was lower in the extrapolation.
With the independent occurrence data at Skrimfjella, we found that neither the *terrain-only* nor *terrain and radiometric* configurations were able to discriminate between peat presence and absence (area under the curve of the receiver operating characteristic 0.44 and 0.52 respectively, where 0.5 indicates random guessing).

### 2024-11-21 ms/ms.tex
ms: results - minor edit extrapolation RMSE

When we tested how well models extrapolated from within to outside of mapped peatland, we found that the models produced marginally better RMSE than just assuming a constant \unit{30\,cm} depth (Fig. \ref{fig:modelMetricsExtrapolation}).
Compared to our error estimates with the full dataset, RMSE at Skrimfjella was nearly unchanged, while at Ørskogfjellet it was lower outside of mapped peatland.
With the independent occurrence data at Skrimfjella, we found that neither the \emph{terrain-only} nor \emph{terrain and radiometric} configurations were able to discriminate between peat presence and absence (area under the curve of the receiver operating characteristic 0.44 and 0.52 respectively, where 0.5 indicates random guessing).

>>>>

When we tested how well models extrapolated from within to outside of mapped peatland, we found that the models produced marginally better RMSE than just assuming a constant \unit{30\,cm} depth (Fig. \ref{fig:modelMetricsExtrapolation}).
At Skrimfjella RMSE in the extrapolation was nearly the same as RMSE across all land cover types.
At Ørskogfjellet RMSE was lower in the extrapolation.
With the independent occurrence data at Skrimfjella, we found that neither the \emph{terrain-only} nor \emph{terrain and radiometric} configurations were able to discriminate between peat presence and absence (area under the curve of the receiver operating characteristic 0.44 and 0.52 respectively, where 0.5 indicates random guessing).
